\LARGE \bf Energy-Aware Dynamic Planning Algorithm for Autonomous UAVs

### 2020-12-14 icra-2021.tex
added a double sized illustrative abstract (turn the first page against light) [Hector and Ulrik are gonna kill me xD]
forgot to include the tex file...
that illustrative abstract is hopefully done now

\usepackage[inline]{enumitem}
\usepackage{booktabs}
\usepackage{flushend}
\usepackage{tikz}
\usetikzlibrary{automata,positioning,decorations.pathreplacing}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry} 
\usepackage{pifont}

@@

\begin{figure}[t]
  \centering
  \input{\figpath/il_abstract.tikz}
  \caption{Illustrative abstract. An initial plan is replanned in terms of both the path and computations.}
  \label{fig:il-abs}
\end{figure}

@@

\leavevmode\thispagestyle{empty}\newpage
\leavevmode\thispagestyle{empty}\newpage % just for now

>>>>

\usepackage[inline]{enumitem}
\usepackage{booktabs}
\usepackage{flushend}
\usepackage{tikz}
\usetikzlibrary{automata,positioning,decorations.pathreplacing,backgrounds}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry} 
\usepackage{pifont}

@@

%\tikz{\fill[blue] (0,0) circle (.7ex);\fill[green] (0,0) -- (90:.7ex) arc (90:270:.7ex) -- cycle;}

\begin{figure}[t]
  \centering
  \definecolor{c00FFFF}{RGB}{0,255,255}
  \input{\figpath/il_abs.tikz}
  \input{\figpath/il_abs_energy.tikz}
  \caption{An initial plan of an agricultural scenario replanned in terms of both the path (\protect\tikz{\fill[white](0,0)circle(.7ex);\fill[blue](0,0)--(90:.7ex)arc(90:270:.7ex)--cycle;}\, travels a more accurate survey than \protect\tikz{\fill[white](0,0)circle(.7ex);\fill[c00FFFF](0,0)--(90:.7ex)arc(90:270:.7ex)--cycle;}) and computations (\protect\tikz{\fill[green](0,0)circle(.7ex);\fill[white](0,0)--(90:.7ex)arc(90:270:.7ex)--cycle;}\, elaborates more images per second than \protect\tikz{\fill[red](0,0)circle(.7ex);\fill[white](0,0)--(90:.7ex)arc(90:270:.7ex)--cycle;}). In bottom right, the collected energy data of the UAV flying the scenario.}
  \label{fig:il-abs}
\end{figure}

@@
